--
title: "Foraging Resilience"
author: "Susan Botha and Alastair Potts"
date: "May 23, 2017"
output:
  html_document: default
  pdf_document: default
---
### IMPORT DATA 

```{r setup}
#knitr::opts_chunk$set(echo = TRUE)

library(dplyr)
library(ggplot2)
library(tidyr)
 
#library(codyn)
#library(tibble)
#library(Rmisc)

# Please copy and paste the working directory code to ALL of your scripts - means 
# I can look into the code faster.
datwd <- "C:\\Users\\susan\\Dropbox\\PhD\\Chp 3 Sust\\Data"
if(Sys.getenv("USER") == "alastair") {datwd <-"/home/alastair/Dropbox/Chp 3 Sust/Data"}
setwd(datwd)

ph <- read.csv("Plots.Harvested.csv",stringsAsFactors = FALSE)
pnh <- read.csv("Plots.NotHarvested.csv",stringsAsFactors = FALSE)
out <- read.csv("OutsidePlot.csv",stringsAsFactors = FALSE)
TtoHarv <- read.csv("PlotSum.csv",stringsAsFactors = FALSE)
plot.info <- read.csv("PlotInfo.csv",stringsAsFactors = FALSE)
codes <- read.csv("CODES.csv",stringsAsFactors = FALSE)

```

## DATE CONVERSION


```{r,echo=F}

# Magical date conversion - always takes me a while to figure out. Useful when plotting! Axes relative to actual dates.
ph <- mutate(ph,Date = as.Date(Date,"%d-%B-%y"))
pnh <- mutate(pnh,Date = as.Date(Date,"%d-%B-%y"))
out <- mutate(out,Date.2016 = as.Date(Date.2016,"%d %m %y"))
codes <-mutate(codes,Date = as.Date(Date,"%d-%B-%y"))
```
### SPECIES HARVESTED REMOVE ABOVEGROUND and Unknown SPP

EXCLUDE berries, seedpod, unknown sp, none 

```{r trimmingph, echo=F}
ph <- ph %>% filter(Part.collected!="berries") %>% filter(Part.collected!="seedpod") %>% filter(Species!="Unknown sp")%>% filter(Species!="None")
```

##Filter out leaves and prionium 
```{r}
ph <- ph %>%filter(Part.collected!="Leaves")%>%filter(Species!="Prionium serratum")%>%select(Date,PlotNo,Species,Edible.weight.g)


```

##SPECIES HARVESTED EXCLUDE UNKNOWN SPECIES
```{r}
ph <- ph %>% filter(Species!="Boophone guttata") %>% filter(Species!="Drimia elata")%>% filter(Species!="Asparagus asparagoides") %>% filter(Species!="Euphorbia burmannii")%>%filter(Species!="Hyacinthaceae") %>% filter(Species!="Ledebouria sp") %>% filter(Species!="wachendorfia speciflora")%>%filter(Species!="Albuca goswinii")%>%filter(Species!="Eriospermum sp")%>%filter(Species!="Unknown sp 1")%>%filter(Species!="Unknown sp 10")%>%filter(Species!="Unknown sp 11")%>%filter(Species!="Unknown sp 2")%>%filter(Species!="Unknown sp 3")%>%filter(Species!="Unknown sp 4")%>%filter(Species!="Unknown sp 5")%>%filter(Species!="Unknown sp 6")%>%filter(Species!="Unknown sp 7")%>%filter(Species!="Unknown sp 8")%>%filter(Species!="Unknown sp 9")%>%filter(Species!="Eriospermum pubescens")

codes <- codes %>% filter(Species!="Boophone guttata") %>% filter(Species!="Drimia elata")%>% filter(Species!="Asparagus asparagoides") %>% filter(Species!="Euphorbia burmannii")%>%filter(Species!="Hyacinthaceae") %>% filter(Species!="Ledebouria sp") %>% filter(Species!="wachendorfia speciflora")%>%filter(Species!="Albuca goswinii")%>%filter(Species!="Eriospermum sp")%>%filter(Species!="Unknown sp 1")%>%filter(Species!="Unknown sp 10")%>%filter(Species!="Unknown sp 11")%>%filter(Species!="Unknown sp 2")%>%filter(Species!="Unknown sp 3")%>%filter(Species!="Unknown sp 4")%>%filter(Species!="Unknown sp 5")%>%filter(Species!="Unknown sp 6")%>%filter(Species!="Unknown sp 7")%>%filter(Species!="Unknown sp 8")%>%filter(Species!="Unknown sp 9")%>%filter(Species!="Eriospermum pubescens")%>%filter(Species!="Mesembryantemum atenus")


write.csv(ph,"C:\\Users\\susan\\Dropbox\\PhD\\Chp 3 Sust\\Results\\depl.roots.csv")

pnh <- pnh %>% filter(Species!="Boophone guttata") %>% filter(Species!="Drimia elata")%>%filter(Species!="Eriospermum pubescens") %>%filter(Species!="Unknown sp 3")%>%filter(Species!="Eriospermum sp")
```
```{r}
##Which codes are most frequently used ##
library(dplyr)
codes%>%group_by(PlotNo,Date,Species,CODE)%>%distinct()%>%summarise(A = sum(CODE=="A"),B=sum(CODE=="B"),C=sum(CODE=="C"),D=sum(CODE=="D"),E=sum(CODE=="E"),F=sum(CODE=="F"),G=sum(CODE=="G"),H=sum(CODE=="H"),I=sum(CODE=="I"))->a

codes%>%group_by(PlotNo,Date,Species,CODE)%>%distinct()%>%summarise(J= sum(CODE=="J"), K=sum(CODE=="K"), L=sum(CODE=="L"), N = sum(CODE=="N"),O=sum(CODE=="O"),V=sum(CODE=="V"))->b


a%>%select(A,B,C,D,E,F,G,H,I)->a
rbind(a,colSums(c[5:13,13]),colSums(a))
```
```{r}
ph
target <- c("Babiana patula","Pelargonium lobatum","Cyphia digitata","Chasmanthe aethiopica","Babiana ambigua","Pelargonium repaceum")
filter(ph, Species %in% target)->T
T%>% mutate(Year = as.numeric(format(Date,"%Y")))%>%group_by(Species,Year)%>%summarise(SSD=sum(Edible.weight.g))->Wt.Pl.Sp

ggplot(Wt.Pl.Sp,aes(x=Species,y=SSD),fill=Year)+geom_bar(stat="identity",position="stack",aes(fill=Year))+
  theme(axis.text.x=element_text(angle=90,hjust=1))


##All species ## 

ph%>% mutate(Year = as.numeric(format(Date,"%Y")))%>%group_by(Species,Year)%>%summarise(SSD=sum(Edible.weight.g))%>%filter(Species!="Gladiolus carinatus")->Wt.Pl.Sp

Wt.Pl.Sp%>%mutate(YearF=factor(Year,levels=c("2015","2016","2017")))->Wt.Pl.Sp

ggplot(Wt.Pl.Sp,aes(x=Species,y=SSD),fill=YearF)+geom_bar(stat="identity",aes(fill=YearF))+theme_classic()+ylab("Edible weight (g)")+scale_fill_grey()+labs(fill="Year")+
  theme(axis.text.x=element_text(angle=90,hjust=1,face = "italic"))->geop.stag
ggsave(filename="C:\\Users\\susan\\Dropbox\\PhD\\Chp 3 Sust\\Results\\GeopStag.jpg",plot=geop.stag,path=NULL,device="jpeg",dpi=600,units="in")
  
```


### Dataset processing

* Within each plot, multiple records were collected per species as there were multiple foragers. These are now summed across species within plots per year.


```{r sumSpp,echo=F}

##TOT WEIGHT PER SPECIES PER YEAR PER PLOT 

hdat2015 <- ph %>% filter(Date < as.Date("2016-01-01")) %>% group_by(Species,PlotNo,Date) %>% summarise(tot.wt = round(sum(Edible.weight.g),1)) %>% rename(Date.2015=Date, tot.wt.2015=tot.wt)%>%na.omit()
                                                                                                        
hdat2016 <- ph %>% filter(Date > as.Date("2016-01-01")) %>% filter(Date < as.Date("2017-01-01" )) %>% group_by(Species,PlotNo,Date) %>% summarise(tot.wt = round(sum(Edible.weight.g),1))%>% rename(Date.2016=Date, tot.wt.2016=tot.wt)%>%na.omit()

hdat2017 <- ph %>% filter(Date > as.Date("2017-01-01")) %>% group_by(Species,PlotNo,Date) %>% summarise(tot.wt = round(sum(Edible.weight.g),1)) %>% rename(Date.2017=Date, tot.wt.2017=tot.wt)%>%na.omit()


full_join(hdat2015,hdat2016,by=c("Species","PlotNo")) %>% full_join(hdat2017,by=c("Species","PlotNo")) -> hdat


###AJP WANT TO REPLACE WITH BLANKS
# Slightly more difficult to remove NA's. Need to use the ifelse(). IF it is NA, then replace with 0, ELSE set to the original value

hdat <- hdat %>% mutate(tot.wt.2015 = ifelse(is.na(tot.wt.2015),0, tot.wt.2015)) %>% mutate(tot.wt.2016 = ifelse(is.na(tot.wt.2016), 0,tot.wt.2016)) %>% mutate(tot.wt.2017 = ifelse(is.na(tot.wt.2017),0, tot.wt.2017))

knitr::kable(hdat,caption="Total weight per species per plot across the three years")

# Create a table with total weights of plants harvested, tot weights per year, percentage per year
hdat %>% group_by(Species) %>% summarise(n=length(unique(PlotNo)),TotalWT = sum(tot.wt.2015,tot.wt.2016,tot.wt.2017),TotWt.2015=sum(tot.wt.2015),TotWt.2016=sum(tot.wt.2016),TotWt.2017=sum(tot.wt.2017)) %>% mutate(PER2015=round(TotWt.2015/TotalWT*100,1),PER2016=round(TotWt.2016/TotalWT*100,1),PER2017=round(TotWt.2017/TotalWT*100,1)) %>% arrange(desc(TotalWT)) -> TABLE1 

###  total weights of plants harvested, tot weights per year, percentage per year broken down by plot number 
hdat %>% group_by(PlotNo) %>% summarise(TotalWT = sum(tot.wt.2015,tot.wt.2016,tot.wt.2017),TotWt.2015=sum(tot.wt.2015),TotWt.2016=sum(tot.wt.2016),TotWt.2017=sum(tot.wt.2017)) %>% mutate(PER2015=round(TotWt.2015/TotalWT*100,1),PER2016=round(TotWt.2016/TotalWT*100,1),PER2017=round(TotWt.2017/TotalWT*100,1)) %>% arrange(desc(PlotNo)) -> TABLE2 

#write.csv(TABLE2, "C:\\Users\\susan\\Dropbox\\PhD\\Chp 3 Sust\\Results\\Fin.Table.Plot.csv",na="")

##excluding Leaves (mesemb and oxalis leaves)
write.csv(TABLE2, "C:\\Users\\susan\\Dropbox\\PhD\\Chp 3 Sust\\Results\\DeplPlotsRoots.csv",na="")


###weight per year across all USO plots 

TABLE2%>%summarise(sum2015=sum(TotWt.2015),sum2016=sum(TotWt.2016),sum2017=sum(TotWt.2017))->TotWtYr



###AVERAGE WEIGHT PER VEG TYPE CONVERTED TO HECTARE ### 

TABLE2
plot.info

right_join(TABLE2,plot.info,by="PlotNo")%>%select(Veg.type,TotalWT,PlotNo)%>%distinct()%>%group_by(Veg.type)%>%summarise(AveWtVt=sum(TotalWT)/1000)
###LESS COLUMNS


##AJP How do you replace the zeros with blanks
#LESS COLUMNS 
TABLE1 %>% select(-TotWt.2015,-TotWt.2016,-TotWt.2017) -> TotProp
#Output
TABLE2 %>% select(PlotNo,TotalWT,PER2015,PER2016,PER2017) -> TotWT.PL

##TOTAL WEIGHT OF ALL USOs ACROSS YEARS 


#Create an object that shows the COUNT of PLANTS harvested 
ph %>% mutate(Year = format(Date,"%Y")) %>% group_by(Species) %>% summarise(No.PLT.HARV = sum(Edible.weight.count)) -> NoPlHv


```

###SPEICES TURNOVER PER PLOT 
```{r}

#Alastair writes his own code so that we can compute spp turnover per plot in one go

species.turnover <- function(species,year) {
  tutu <- as.data.frame.matrix(table(species,year))
  if (sum(tutu>1)>0) stop("There are replicated rows for each species per year. Please fix.")
  if (ncol(tutu)>2) stop("Ensure that only two years are fed into this function. Please fix.")
  if (length(unique(year))!=2) return(NA)
  gain <- sum((tutu[,1]==F)&(tutu[,2]==T))
  lost <- sum((tutu[,1]==T)&(tutu[,2]==F))
  tot <- nrow(tutu)  
  return(round((gain+lost)/tot,3))
}

# CAlculates the SPP TURNOVER Between 2015 & 2016, 2016 & 2017, 2015 & 2017
# 2015 vs 2016 

ph %>% mutate(Year = as.numeric(format(Date,"%Y")))%>%select(Species,Year,PlotNo,Edible.weight.g,Edible.weight.count) %>% filter(Species!="Unknown sp")%>% group_by(Species,Year,PlotNo) %>% summarise(Edible.weight.g=sum(Edible.weight.g,na.rm=T),Edible.weight.count=sum(Edible.weight.count,na.rm=T)) %>% filter(Year!=2017)%>% group_by(PlotNo) %>%summarise(turnover15.16=species.turnover(Species,Year)) -> Turn.15.16

# 2016 vs 2017   

ph %>% mutate(Year = as.numeric(format(Date,"%Y")))%>%select(Species,Year,PlotNo,Edible.weight.g,Edible.weight.count) %>% filter(Species!="Unknown sp")%>% group_by(Species,Year,PlotNo) %>% summarise(Edible.weight.g=sum(Edible.weight.g,na.rm=T),Edible.weight.count=sum(Edible.weight.count,na.rm=T)) %>% filter(Year!=2015) %>% group_by(PlotNo)%>%summarise(turnover16.17=species.turnover(Species,Year)) -> Turn.16.17
 
# 2015 vs 2017 

ph %>% mutate(Year = as.numeric(format(Date,"%Y")))%>%select(Species,Year,PlotNo,Edible.weight.g,Edible.weight.count) %>% filter(Species!="Unknown sp")%>% group_by(Species,Year,PlotNo) %>% summarise(Edible.weight.g=sum(Edible.weight.g,na.rm=T),Edible.weight.count=sum(Edible.weight.count,na.rm=T)) %>% filter(Year!=2016)%>% group_by(PlotNo) %>%summarise(turnover15.17=species.turnover(Species,Year)) -> Turn.15.17

## CREATE new table which shows SPP TURNOVER for all three these years per plot 

full_join(Turn.15.16,Turn.16.17,by="PlotNo") -> TO1
full_join(TO1,Turn.15.17,by="PlotNo") -> TO2

full_join(TO2,TotWT.PL,by="PlotNo") -> FIN.TABLE.PLOT

##ADD VEG TYPE

###right_join(FIN.TABLE.PLOT,plot.info,by="PlotNo")%>%select(Veg.type,PlotNo,turn  distinct()

write.csv(FIN.TABLE.PLOT,"C:\\Users\\susan\\Dropbox\\PhD\\Chp 3 Sust\\Results\\FIN.TABLE.PLOT.csv",na="")


##Create one column for species turnover 

# Alastair frowns upon the shift of across year nomenclanture to a single year
#CDiv.Prop.Spp %>% select (PlotNo,turnover15.16,turnover16.17,turnover15.17)%>% gather(CDiv.Prop.Spp,Spp.TOVER.Year,turnover15.16,turnover15.17,turnover16.17)%>% dplyr::rename(Turnover.Period="CDiv.Prop.Spp")%>%
  #mutate(Turnover.Period=gsub("turnover15.16","2015",Turnover.Period),
        # Turnover.Period=gsub("turnover16.17","2016",Turnover.Period),
         #Turnover.Period=gsub("turnover15.17","2017",Turnover.Period)) -> TOverYear -> Turnover

##CREATE ONE COLUMN for PercWtYear
CDiv.Prop.Spp %>% select(PlotNo,P2015,P2016,P2017)%>% gather(CDiv.Prop.Spp,Perc.Wt.Yr,P2015,P2017,P2016) -> PercWtYear

###CREATE ONE COLUMN FOR TIME TO HARVEST
TtoHarv%>%select(PlotNo,Time2015,Time2016,Time2017)%>%gather(TtoHarv,Time,Time2015,Time2016,Time2017) ->  TtoHarvs

###CREATE ONE COLumn FOR EDIBLE WT PER YEAR
Wt.P.Plot%>%select(PlotNo,Y2015,Y2016,Y2017)%>%gather(Wt.P.Plot,Wt.Plot,Y2015,Y2016,Y2017) ->  Wt.P.Plot.T

##AJP
 # PRETTIFYING BEFORE PRINTING (DO THIS TO ADD A YEAR COLUMN)

# TOverYear <-  write.csv(TOverYear,"C:\\Users\\susan\\Dropbox\\PhD\\Chp 3 Sust\\Results\\TOverYear.csv",na="")
# PercWtYear <-  write.csv(PercWtYear,"C:\\Users\\susan\\Dropbox\\PhD\\Chp 3 Sust\\Results\\PercWtYear.csv",na="")
write.csv(TtoHarv,"C:\\Users\\susan\\Dropbox\\PhD\\Chp 3 Sust\\Results\\TtoHarvs.csv",na="")
# Wt.P.Plot.T <- write.csv(Wt.P.Plot.T,"C:\\Users\\susan\\Dropbox\\PhD\\Chp 3 Sust\\Results\\Wt.P.Plot.T.csv",na="")
```


```{r}
##TOT COUNT HARVESTED PER BOUT
##NAS need to always be set to zero !!! 

cdat2015 <- ph %>% filter(Date < as.Date("2016-01-01" )) %>% group_by(Species,PlotNo,Date) %>% summarise(count = round(sum(Edible.weight.count),1)) %>% rename(Date.2015=Date, Harv.2015=count)
                                                                                                        
cdat2016 <- ph %>% filter(Date > as.Date("2016-01-01" )) %>% filter(Date < as.Date("2017-01-01" )) %>% group_by(Species,PlotNo,Date) %>% summarise(count = round(sum(Edible.weight.count),1))%>% rename(Date.2016=Date, Harv.2016=count)

cdat2017 <- ph %>% filter(Date > as.Date("2017-01-01")) %>% group_by(Species,PlotNo,Date) %>% summarise(count = round(sum(Edible.weight.count),1)) %>% rename(Date.2017=Date, Harv.2017=count)

###COUNT OF EDIBLE PLANTS THAT WERE HARVESTED
cdat <- full_join(cdat2015,cdat2016,by=c("Species","PlotNo")) %>% full_join(y=cdat2017,by=c("Species","PlotNo")) -> totc

###

totc %>% group_by(Species) %>% summarise(n=length(unique(PlotNo)),TotalC = sum(Harv.2015,Harv.2016,Harv.2017,na.rm=T),Harv.2015=sum(Harv.2015,na.rm=T),Harv.2016=sum(Harv.2016,na.rm=T),Harv.2017=sum(Harv.2017,na.rm=T)) -> TOTPLHV


#cdat <- cdat %>% mutate(count.2015 = ifelse(is.na(count.2015),0, count.2015)) %>% mutate(count.2016 = ifelse(is.na(count.2016), 0,count.2016)) %>% mutate(count.2017 = ifelse(is.na(count.2017),0, count.2017))

knitr::kable(cdat,caption="Total weight per species per plot across the three years")

```

### PLANTS LEFT BEHIND 

```{r}
#Create two objects that shows no of plants left behind (PlNotDug) and reasons why per year(Why)

pnh %>% mutate(Year = format(Date,"%Y")) %>% group_by(Species,PlotNo,Year)%>% summarise(Not.Harv.tot=sum(No.of.plants.not.dug.up))%>%spread(Year,Not.Harv.tot)%>%rename(NH2015="2015",NH2016="2016",NH2017="2017")->totNH
  
totNH%>%group_by(Species)%>%summarise(n=unique(length(PlotNo)),NotHarv2015=sum(NH2015, na.rm=T),NotHarv2016=sum(NH2016,na.rm=T),NotHarv2017=sum(NH2017,na.rm=T))->PlNotDug

                                        
                                         
pnh %>% mutate(Year = format(Date,"%Y")) %>% group_by(Species,Year) %>% summarise(Code = paste(Constraint,collapse=","))%>% spread(Year, Code) -> Why

# Create a table with these two objects 

full_join(PlNotDug,Why,by='Species') %>% dplyr:: rename(C2015="2015",C2016="2016",C2017="2017") %>% select("Species","NotHarv2015","NotHarv2016","NotHarv2017","C2017","C2015","C2016") -> TBNH


#Create a new table that shows joins Total Weights and yearly proportions to the no of plants bit dug up and reasons why (CODE)

full_join(TotProp,TOTPLHV, by="Species") -> TBHV
full_join(TBHV,TBNH,by="Species") ->  FIN.TBL
FIN.TBL%>%mutate(Prop.NH2015=(NotHarv2015/(Harv.2015+NotHarv2015)*100),Prop.NH2016=(NotHarv2016/(Harv.2016+NotHarv2016)*100),PropNH2017=(NotHarv2017/(Harv.2017+NotHarv2017)*100)) -> FIN.TBL

write.csv(FIN.TBL,"C:\\Users\\susan\\Dropbox\\PhD\\Chp 3 Sust\\Results\\FIN.TBLE.SPP.csv",na="")

```

### TIME SERIES ANOVA

##CREATE A TABLE THAT SHOWS PERCENTAGE OF PLANTS LEFT BEHIND PER PLOT PER YEAR
##AND WHY


```{r}
pnh %>% mutate(Year = format(Date,"%Y")) %>% group_by(Species,Year,PlotNo) %>% summarise(COUNT = sum(No.of.plants.not.dug.up)) %>% spread(Year,COUNT)%>%rename(NotHarv.2015="2015",NotHarv.2016="2016",NotHarv.2017="2017") -> PlPLotNotDug

Prop.Pl.Not.Hrv <- full_join(PlPLotNotDug,cdat,by=c("PlotNo","Species"))
full_join(Prop.Pl.Not.Hrv,Why,by=c("PlotNo","Species")) -> Prop.Pl.Not.Hrv.W

Prop.Left.BeH.W <- Prop.Pl.Not.Hrv.W %>%mutate(Prop2015=(NotHarv.2015/Harv.2015))%>%mutate(Prop2016=(NotHarv.2016/Harv.2016))%>%mutate(Prop2017=(NotHarv.2017/Harv.2017))%>%select(-Date.2015,-Date.2016,-Date.2017)

write.csv(Prop.Left.BeH.W,"C:\\Users\\susan\\Dropbox\\PhD\\Chp 3 Sust\\Results\\Prop.Left.BeH.W.csv",na="")

```


### Determine EDIBLE WEIGHT PER PLOT PER YEAR 

```{r}
ph %>% mutate(Year = format(Date,"%Y")) %>% group_by(PlotNo,Year) %>% summarise(Tot.Wt.Pl = round(sum(Edible.weight.g,na.rm=TRUE),1)) %>% spread(Year,Tot.Wt.Pl) %>% dplyr::rename(Y2015="2015", Y2016="2016",Y2017="2017") -> Wt.Plot
                                                                                                                                                    

Wt.Plot %>% mutate(TOT = sum(Y2015,Y2016,Y2017,na.rm=T),P2015=round((Y2015/TOT),2),P2016=round((Y2016/TOT),2),P2017=round((Y2017/TOT),2)) -> Wt.P.Plot


write.csv(Wt.P.Plot,"C:\\Users\\susan\\Dropbox\\PhD\\Chp 3 Sust\\Results\\Wt.P.Plot.csv",na="")


```


# DEtermine turnover of species for every plot 


```

#CREATE PERWtYEAr for each plot 

```{r}
#filter depletion plots
Depld.Plots <- read.csv("C:\\Users\\susan\\Dropbox\\PhD\\Chp 3 Sust\\Results\\PercWtYear.Y.csv",stringsAsFactors = TRUE)
#Depld.Plots <- data.matrix(Depld.Plots, rownames.force = NA)


Plot01 <- Depld.Plots%>% filter(PlotNo=="Plot01")
Plot02 <- Depld.Plots%>% filter(PlotNo=="Plot02")
Plot05 <- Depld.Plots%>% filter(PlotNo=="Plot05")
Plot06 <- Depld.Plots%>% filter(PlotNo=="Plot06")
Plot07 <- Depld.Plots%>% filter(PlotNo=="Plot07")
Plot08 <- Depld.Plots%>% filter(PlotNo=="Plot08")
Plot09 <- Depld.Plots%>% filter(PlotNo=="Plot09")
Plot10 <- Depld.Plots%>% filter(PlotNo=="Plot10")
Plot11 <- Depld.Plots%>% filter(PlotNo=="Plot11")
Plot12 <- Depld.Plots%>% filter(PlotNo=="Plot12")
Plot13 <- Depld.Plots%>% filter(PlotNo=="Plot13")
Plot14 <- Depld.Plots%>% filter(PlotNo=="Plot14")
Plot15 <- Depld.Plots%>% filter(PlotNo=="Plot15")
Plot16 <- Depld.Plots%>% filter(PlotNo=="Plot16")
Plot17 <- Depld.Plots%>% filter(PlotNo=="Plot17")
Plot18 <- Depld.Plots%>% filter(PlotNo=="Plot18")
Plot19 <- Depld.Plots%>% filter(PlotNo=="Plot19")
Plot20 <- Depld.Plots%>% filter(PlotNo=="Plot20")
#filter stochastic plots
Plot03 <- Depld.Plots%>% filter(PlotNo=="Plot03")
Plot04 <- Depld.Plots%>% filter(PlotNo=="Plot04")
```

### Create Turnover per plot

```{r}
Turnover <- read.csv("C:\\Users\\susan\\Dropbox\\PhD\\Chp 3 Sust\\Results\\TOverYear.Y.csv")

Plot01T <-Turnover%>%filter(PlotNo=="Plot01")
Plot02T <-Turnover%>%filter(PlotNo=="Plot02")
Plot03T <-Turnover%>%filter(PlotNo=="Plot03")
Plot04T <-Turnover%>%filter(PlotNo=="Plot04")
Plot05T <-Turnover%>%filter(PlotNo=="Plot05")
Plot06T <-Turnover%>%filter(PlotNo=="Plot06")
Plot07T <-Turnover%>%filter(PlotNo=="Plot07")
Plot08T <-Turnover%>%filter(PlotNo=="Plot08")
Plot09T <-Turnover%>%filter(PlotNo=="Plot09")
Plot10T <-Turnover%>%filter(PlotNo=="Plot10")
Plot11T <-Turnover%>%filter(PlotNo=="Plot11")
Plot12T <-Turnover%>%filter(PlotNo=="Plot12")
Plot13T <-Turnover%>%filter(PlotNo=="Plot13")
Plot14T <-Turnover%>%filter(PlotNo=="Plot14")
Plot15T <-Turnover%>%filter(PlotNo=="Plot15")
Plot17T <-Turnover%>%filter(PlotNo=="Plot17")
Plot16T <-Turnover%>%filter(PlotNo=="Plot16")

Plot18T <-Turnover%>%filter(PlotNo=="Plot18")
Plot19T <-Turnover%>%filter(PlotNo=="Plot19")
Plot20T <-Turnover%>%filter(PlotNo=="Plot20")
```

###CREATE TIME TAKEN TO HARVEST 
```{r}
TtoHarvs <- read.csv("C:\\Users\\susan\\Dropbox\\PhD\\Chp 3 Sust\\Results\\TtoHarvs.1.csv")

Plot01TH <-TtoHarvs%>%filter(PlotNo=="Plot01")
Plot02TH <-TtoHarvs%>%filter(PlotNo=="Plot02")%>%arrange(desc(Year))
Plot03TH <-TtoHarvs%>%filter(PlotNo=="Plot03")
Plot04TH <-TtoHarvs%>%filter(PlotNo=="Plot04")
Plot05TH <-TtoHarvs%>%filter(PlotNo=="Plot05")
Plot06TH <-TtoHarvs%>%filter(PlotNo=="Plot06")
Plot07TH <-TtoHarvs%>%filter(PlotNo=="Plot07")
Plot08TH <-TtoHarvs%>%filter(PlotNo=="Plot08")
Plot09TH <-TtoHarvs%>%filter(PlotNo=="Plot09")
Plot10TH <-TtoHarvs%>%filter(PlotNo=="Plot10")
Plot11TH <-TtoHarvs%>%filter(PlotNo=="Plot11")
Plot12TH <-TtoHarvs%>%filter(PlotNo=="Plot12")
Plot13TH <-TtoHarvs%>%filter(PlotNo=="Plot13")
Plot14TH <-TtoHarvs%>%filter(PlotNo=="Plot14")
Plot15TH <-TtoHarvs%>%filter(PlotNo=="Plot15")
Plot16TH <-TtoHarvs%>%filter(PlotNo=="Plot16")
Plot17TH <-TtoHarvs%>%filter(PlotNo=="Plot17")
Plot18TH <-TtoHarvs%>%filter(PlotNo=="Plot18")
Plot19TH <-TtoHarvs%>%filter(PlotNo=="Plot19")
Plot20TH <-TtoHarvs%>%filter(PlotNo=="Plot20")
```
##PLOTTING TIME TO HARVEST SEPARATELY

```{r}
PlTH1 <- ggplot()+geom_line(data=Plot01TH,aes(x=Year,y=Time),group=1,colour='blue')
PlTH2 <- ggplot()+geom_line(data=Plot02TH,aes(x=Year,y=Time),group=1,colour='blue')
PlTH3 <- ggplot()+geom_line(data=Plot03TH,aes(x=Year,y=Time),group=1,colour='blue')
```


### PLOT DEPLETED PLOTS

```{r}
#PLot 01

Pl1 <- ggplot()+geom_line(data=Plot01,aes(x=Year,y=Perc.Wt.Yr),size=1,colour="black")+geom_line(data=Plot01T,aes(x=Year,y=Spp.TOVER.Year),colour='red',size=1)+labs(x="Year",y="Percentage %")+
  #theme(plot.title = element_text(margin = margin(b = 0)))+
  annotate("text", x = 2015.1, y = 0.9, label = "Plot 01",)+
  scale_x_continuous(breaks =c(2015,2016,2017),
                     sec.axis = sec_axis(~ ., breaks=c(2015,2016,2017),labels=c("15/16","16/17","15/17")))+
  theme(legend.position = "right")
print(Pl1)
              
```



```{r}

#ggplot(Wt.P.Plot.2)+geom_line(data=Wt.P.Plot.2,aes(x=(Plot01=filter(PlotNo==Plot01)%>%Plot01$Year)),y=P2015)

#PLot 01

Pl1 <- ggplot()+geom_line(data=Plot01,aes(x=Year,y=Perc.Wt.Yr),size=1,colour="black")+geom_line(data=Plot01T,aes(x=Year,y=Spp.TOVER.Year),colour='red',size=1)+labs(title="Plot01",x="Year",y="Percentage %")+theme(plot.title = element_text(margin = margin(b = -20)))+scale_x_continuous(breaks =c(2015,2016,2017))+theme(legend.position = "right")
              

ggsave(filename="C:\\Users\\susan\\Dropbox\\PhD\\Chp 3 Sust\\Results\\Pl1.jpeg",plot=last_plot(),path=NULL,device="jpeg",dpi=600,width=12,height=12,units="cm")
print(Pl1)
dev.off()


#Plot 02

Pl2 <- ggplot()+geom_line(data=Plot02,aes(x=Year,y=Perc.Wt.Yr),size=1)+geom_line(data=Plot02T,aes(x=Year,y=Spp.TOVER.Year),colour='red',size=1)+labs(title="Plot02",x="Year",y="Percentage of total weight harvested")+theme(plot.title = element_text(margin = margin(b = -20))) 
ggsave(filename="C:\\Users\\susan\\Dropbox\\PhD\\Chp 3 Sust\\Results\\Pl2.jpeg",plot=last_plot(),path=NULL,device="jpeg",dpi=600,width=12,height=12,units="cm")
print(Pl2)
dev.off()


#Plot 05
Pl5 <- ggplot()+geom_line(data=Plot05,aes(x=Year,y=Perc.Wt.Yr),size=1)+geom_line(data=Plot05T,aes(x=Year,y=Spp.TOVER.Year),colour='red',size=1)+labs(title="Plot05",x="Year",y="Percentage of total weight harvested")+theme(plot.title = element_text(margin = margin(b = -20))) 
ggsave(filename="C:\\Users\\susan\\Dropbox\\PhD\\Chp 3 Sust\\Results\\Pl5.jpeg",plot=last_plot(),path=NULL,device="jpeg",dpi=600,width=12,height=12,units="cm")
print(Pl5)
dev.off()

#Plot 06
Pl6 <- ggplot()+geom_line(data=Plot06,aes(x=Year,y=Perc.Wt.Yr),size=1)+geom_line(data=Plot06T,aes(x=Year,y=Spp.TOVER.Year),colour='red',size=1)+labs(title="Plot06",x="Year",y="Percentage of total weight harvested")+theme(plot.title = element_text(margin = margin(b = -20)))
ggsave(filename="C:\\Users\\susan\\Dropbox\\PhD\\Chp 3 Sust\\Results\\Pl6.jpeg",plot=last_plot(),path=NULL,device="jpeg",dpi=600,width=12,height=12,units="cm")
print(Pl6)
dev.off()

#Plot 07
Pl7 <- ggplot()+geom_line(data=Plot07,aes(x=Year,y=Perc.Wt.Yr),size=1)+geom_line(data=Plot07T,aes(x=Year,y=Spp.TOVER.Year),colour='red',size=1)+labs(title="Plot07",x="Year",y="Percentage of total weight harvested")+theme(plot.title = element_text(margin = margin(b = -20)))
ggsave(filename="C:\\Users\\susan\\Dropbox\\PhD\\Chp 3 Sust\\Results\\Pl7.jpeg",plot=last_plot(),path=NULL,device="jpeg",dpi=600,width=12,height=12,units="cm")
print(Pl7)
dev.off()

#Plot 08
Pl8 <- ggplot()+geom_line(data=Plot08,aes(x=Year,y=Perc.Wt.Yr),size=1)+geom_line(data=Plot08T,aes(x=Year,y=Spp.TOVER.Year),colour='red',size=1)+labs(title="Plot08",x="Year",y="Percentage of total weight harvested")+theme(plot.title = element_text(margin = margin(b = -20)))
ggsave(filename="C:\\Users\\susan\\Dropbox\\PhD\\Chp 3 Sust\\Results\\Pl8.jpeg",plot=last_plot(),path=NULL,device="jpeg",dpi=600,width=12,height=12,units="cm")
print(Pl8)
dev.off()

#Plot 09
Pl9 <- ggplot()+geom_line(data=Plot09,aes(x=Year,y=Perc.Wt.Yr),size=1)+geom_line(data=Plot09T,aes(x=Year,y=Spp.TOVER.Year),colour='red',size=1)+labs(title="Plot09",x="Year",y="Percentage of total weight harvested")+theme(plot.title = element_text(margin = margin(b = -20)))
ggsave(filename="C:\\Users\\susan\\Dropbox\\PhD\\Chp 3 Sust\\Results\\Pl9.jpeg",plot=last_plot(),path=NULL,device="jpeg",dpi=600,width=12,height=12,units="cm")
print(Pl9)
dev.off()

#Plot 10
Pl10 <- ggplot()+geom_line(data=Plot10,aes(x=Year,y=Perc.Wt.Yr),size=1)+geom_line(data=Plot10T,aes(x=Year,y=Spp.TOVER.Year),colour='red',size=1)+labs(title="Plot10",x="Year",y="Percentage of total weight harvested")+theme(plot.title = element_text(margin = margin(b = -20)))
ggsave(filename="C:\\Users\\susan\\Dropbox\\PhD\\Chp 3 Sust\\Results\\Pl10.jpeg",plot=last_plot(),path=NULL,device="jpeg",dpi=600,width=12,height=12,units="cm")
print(Pl10)
dev.off()

#Plot 11
Pl11 <- ggplot()+geom_line(data=Plot11,aes(x=Year,y=Perc.Wt.Yr),size=1)+geom_line(data=Plot11T,aes(x=Year,y=Spp.TOVER.Year),colour='red',size=1)+labs(title="Plot11",x="Year",y="Percentage of total weight harvested")+theme(plot.title = element_text(margin = margin(b = -20)))
ggsave(filename="C:\\Users\\susan\\Dropbox\\PhD\\Chp 3 Sust\\Results\\Pl11.jpeg",plot=last_plot(),path=NULL,device="jpeg",dpi=600,width=12,height=12,units="cm")
print(Pl11)
dev.off()

#Plot 12
Pl12 <- ggplot()+geom_line(data=Plot12,aes(x=Year,y=Perc.Wt.Yr),size=1)+geom_line(data=Plot12T,aes(x=Year,y=Spp.TOVER.Year),colour='red',size=1)+labs(title="Plot12",x="Year",y="Percentage of total weight harvested")+theme(plot.title = element_text(margin = margin(b = -20)))
ggsave(filename="C:\\Users\\susan\\Dropbox\\PhD\\Chp 3 Sust\\Results\\Pl12.jpeg",plot=last_plot(),path=NULL,device="jpeg",dpi=600,width=12,height=12,units="cm")
print(Pl12)
dev.off()

#Plot 13 
Pl13 <- ggplot()+geom_line(data=Plot13,aes(x=Year,y=Perc.Wt.Yr),size=1)+geom_line(data=Plot13T,aes(x=Year,y=Spp.TOVER.Year),colour='red',size=1)+labs(title="Plot13",x="Year",y="Percentage of total weight harvested")+theme(plot.title = element_text(margin = margin(b = -20)))
ggsave(filename="C:\\Users\\susan\\Dropbox\\PhD\\Chp 3 Sust\\Results\\Pl13.jpeg",plot=last_plot(),path=NULL,device="jpeg",dpi=600,width=12,height=12,units="cm")
print(Pl13)
dev.off()

#Plot 14
Pl14 <- ggplot()+geom_line(data=Plot14,aes(x=Year,y=Perc.Wt.Yr),size=1)+geom_line(data=Plot14T,aes(x=Year,y=Spp.TOVER.Year),colour='red',size=1)+labs(title="Plot14",x="Year",y="Percentage of total weight harvested")+theme(plot.title = element_text(margin = margin(b = -20)))
ggsave(filename="C:\\Users\\susan\\Dropbox\\PhD\\Chp 3 Sust\\Results\\Pl14.jpeg",plot=last_plot(),path=NULL,device="jpeg",dpi=600,width=12,height=12,units="cm")
print(Pl14)
dev.off()

#Plot 15
Pl15 <- ggplot()+geom_line(data=Plot15,aes(x=Year,y=Perc.Wt.Yr),size=1)+geom_line(data=Plot15T,aes(x=Year,y=Spp.TOVER.Year),colour='red',size=1)+labs(title="Plot15",x="Year",y="Percentage of total weight harvested")+theme(plot.title = element_text(margin = margin(b = -20)))
ggsave(filename="C:\\Users\\susan\\Dropbox\\PhD\\Chp 3 Sust\\Results\\Pl15.jpeg",plot=last_plot(),path=NULL,device="jpeg",dpi=600,width=12,height=12,units="cm")
print(Pl15)
dev.off()

#Plot 16
Pl16 <- ggplot()+geom_line(data=Plot16,aes(x=Year,y=Perc.Wt.Yr),size=1)+geom_line(data=Plot16T,aes(x=Year,y=Spp.TOVER.Year),colour='red',size=1)+labs(title="Plot16",x="Year",y="Percentage of total weight harvested")+theme(plot.title = element_text(margin = margin(b = -20)))
ggsave(filename="C:\\Users\\susan\\Dropbox\\PhD\\Chp 3 Sust\\Results\\Pl16.jpeg",plot=last_plot(),path=NULL,device="jpeg",dpi=600,width=12,height=12,units="cm")
print(Pl16)
dev.off()

#Plot 17

Pl17 <- ggplot()+geom_line(data=Plot17,aes(x=Year,y=Perc.Wt.Yr),size=1)+geom_line(data=Plot17T,aes(x=Year,y=Spp.TOVER.Year),colour='red',size=1)+labs(title="Plot17",x="Year",y="Percentage of total weight harvested")+theme(plot.title = element_text(margin = margin(b = -20)))
ggsave(filename="C:\\Users\\susan\\Dropbox\\PhD\\Chp 3 Sust\\Results\\Pl17.jpeg",plot=last_plot(),path=NULL,device="jpeg",dpi=600,width=12,height=12,units="cm")
print(Pl17)
dev.off()

#Plot 18
Pl18 <- ggplot()+geom_line(data=Plot18,aes(x=Year,y=Perc.Wt.Yr),size=1)+geom_line(data=Plot18T,aes(x=Year,y=Spp.TOVER.Year),colour='red',size=1)+labs(title="Plot18",x="Year",y="Percentage of total weight harvested")+theme(plot.title = element_text(margin = margin(b = -20)))
ggsave(filename="C:\\Users\\susan\\Dropbox\\PhD\\Chp 3 Sust\\Results\\Pl18.jpeg",plot=last_plot(),path=NULL,device="jpeg",dpi=600,width=12,height=12,units="cm")
print(Pl8)
dev.off()

#Plot 19
Pl19 <- ggplot()+geom_line(data=Plot19,aes(x=Year,y=Perc.Wt.Yr),size=1)+geom_line(data=Plot19T,aes(x=Year,y=Spp.TOVER.Year),colour='red',size=1)+labs(title="Plot19",x="Year",y="Percentage of total weight harvested")+theme(plot.title = element_text(margin = margin(b = -20)))
ggsave(filename="C:\\Users\\susan\\Dropbox\\PhD\\Chp 3 Sust\\Results\\Pl19.jpeg",plot=last_plot(),path=NULL,device="jpeg",dpi=600,width=12,height=12,units="cm")
print(Pl19)
dev.off()

#Plot 20
Pl20 <- ggplot()+geom_line(data=Plot20,aes(x=Year,y=Perc.Wt.Yr),size=1)+geom_line(data=Plot20T,aes(x=Year,y=Spp.TOVER.Year),colour='red',size=1)+labs(title="Plot20",x="Year",y="Percentage of total weight harvested")+theme(plot.title = element_text(margin = margin(b = -20)))
ggsave(filename="C:\\Users\\susan\\Dropbox\\PhD\\Chp 3 Sust\\Results\\Pl20.jpeg",plot=last_plot(),path=NULL,device="jpeg",dpi=600,width=12,height=12,units="cm")
print(Pl20)
dev.off()


###STOCHASTIC PLOTS
#Plot 03
Pl3 <- ggplot()+geom_line(data=Plot03,aes(x=Year,y=Perc.Wt.Yr),size=1)+geom_line(data=Plot03T,aes(x=Year,y=Spp.TOVER.Year),colour='red',size=1)+ggtitle("Plot03")+labs(title="Plot03",x="Year",y="Percentage of total weight harvested")+theme(plot.title = element_text(margin = margin(b = -20)))
ggsave(filename="C:\\Users\\susan\\Dropbox\\PhD\\Chp 3 Sust\\Results\\Pl03.jpeg",plot=last_plot(),path=NULL,device="jpeg",dpi=600,width=12,height=12,units="cm")
print(Pl3)
dev.off()

#Plot 04
Pl4 <- ggplot()+geom_line(data=Plot04,aes(x=Year,y=Perc.Wt.Yr),size=1)+geom_line(data=Plot04T,aes(x=Year,y=Spp.TOVER.Year),colour='red',size=1)+labs(title="Plot04",x="Year",y="Percentage of total weight harvested")+theme(plot.title = element_text(margin = margin(b = -20)))
ggsave(filename="C:\\Users\\susan\\Dropbox\\PhD\\Chp 3 Sust\\Results\\Pl4.jpeg",plot=last_plot(),path=NULL,device="jpeg",dpi=600,width=12,height=12,units="cm")
print(Pl4)
dev.off()


```
### Multiple plots

```{r}

#Plot 06
Pl6.10.11 <- ggplot()+geom_line(data=Plot06,aes(x=Year,y=Perc.Wt.Yr),size=1)+geom_line(data=Plot06T,aes(x=Year,y=Spp.TOVER.Year),colour='red',size=1)+geom_line(data=Plot10,aes(x=Year,y=Perc.Wt.Yr),colour='blue',size=1)+geom_line(data=Plot11,aes(x=Year,y=Perc.Wt.Yr),colour='green',size=1)+labs(title="Plot06",x="Year",y="Percentage of total weight harvested")+theme(plot.title = element_text(margin = margin(b = -20)))
ggsave(filename="C:\\Users\\susan\\Dropbox\\PhD\\Chp 3 Sust\\Results\\Pl6.jpeg",plot=last_plot(),path=NULL,device="jpeg",dpi=600,width=12,height=12,units="cm")
print(Pl6)
dev.off()
ggsave(filename="C:\\Users\\susan\\Dropbox\\PhD\\Chp 3 Sust\\Results\\PlDPlts.jpg",plot=Pl1,path=NULL,device="jpeg",dpi=600,width=12,height=18,units="in")
dev.off()

```



### TIME SERIES ANOVA TO TEST DIFFERENCE IN TOTAL WEIGHT HARVESTED BETWEEN THE THREE YEARS


### Unique species

```{r}
library(ggub)
ph %>% select(Species,Part.collected)%>%distinct(Species,Part.collected) %>% filter(Species!="Zero")-> uniq.sp

write.csv(uniq.sp,file="C:\\Users\\susan\\Dropbox\\PhD\\Chp 3 Sust\\Data\\GeophyteMorphology.csv")
```

### Unique species per plot per year 


### GRAPHS THAT VISUALLY SHOW THE PLANTS HARVESTED ACROSS THREE YEARS 

```{r}
hdat$SppName<-unlist(lapply(lapply(strsplit(hdat$Species," "),substr,1,3),paste,collapse=""))
hdat <- arrange(hdat,PlotNo,Species)

## GRAPH: 2015 vs 2016 WITH names 
ggplot(hdat, aes(x=tot.wt.2015+0.1,y=tot.wt.2016+0.1,label=hdat$SppName)) +
  scale_x_log10(breaks=c(0.1,1,10,100,1000),labels=c(0,1,10,100,1000))+
  scale_y_log10(breaks=c(0.1,1,10,100,1000),labels=c(0,1,10,100,1000))+
  geom_text_repel()+
  #geom_point(aes(shape=Outside.2016,colour=Outside.2016),size=2,show.legend=T)+
  geom_point() +
  #scale_shape_manual(values=20)+
  geom_abline(slope=1,intercept=0,lty=2) +
  xlab("2015 Harvest (g; log-scale)")+
  ylab("2016 Harvest (g; log-scale)")+
  labs(group="In Landscape")+
  coord_fixed()+
  theme(legend.position = "right")
#dev.off()

## GRAPH: 2015 vs 2016 WITHOUT names 

jpeg(filename ="C:\\Users\\susan\\Dropbox\\PhD\\Chp 3 Sust\\Harvest2015vs2016nolabs.jpg",res=300,width=12,height=12,units="cm")
ggplot(hdat, aes(x=tot.wt.2015+0.1,y=tot.wt.2016+0.1)) +
  scale_x_log10(breaks=c(0.1,1,10,100,1000),labels=c(0,1,10,100,1000))+
  scale_y_log10(breaks=c(0.1,1,10,100,1000),labels=c(0,1,10,100,1000))+
  #geom_point(aes(shape=Outside.2016,colour=Outside.2016),size=2,show.legend=T)+
  geom_point() +
  #scale_shape_manual(values=20)+
  geom_abline(slope=1,intercept=0,lty=2) +
  xlab("2015 Harvest (g; log-scale)")+
  ylab("2016 Harvest (g; log-scale)")+
  labs(group="In Landscape")+
  coord_fixed()+
  theme(legend.position = "right")
dev.off()

# GRAPH: 2017 vs 2016 WITH SPECIES Name 

ggplot(hdat, aes(x=tot.wt.2017+0.1,y=tot.wt.2016+0.1,label=hdat$SppName)) +
  scale_x_log10(breaks=c(0.1,1,10,100,1000),labels=c(0,1,10,100,1000))+
  scale_y_log10(breaks=c(0.1,1,10,100,1000),labels=c(0,1,10,100,1000))+
  geom_text_repel()+
  #geom_point(aes(shape=Outside.2016,colour=Outside.2016),size=2,show.legend=T)+
  geom_point() +
  #scale_shape_manual(values=20)+
  geom_abline(slope=1,intercept=0,lty=2) +
  xlab("2017 Harvest (g; log-scale)")+
  ylab("2016 Harvest (g; log-scale)")+
  labs(group="In Landscape")+
  coord_fixed()+
  theme(legend.position = "right")
#dev.off()

## GRAPH: 2017 vs 2016 WITHOUT Species names 

jpeg(filename ="C:\\Users\\susan\\Dropbox\\PhD\\Chp 3 Sust\\Results\\Harvest2016vs2017nolabs.jpg",res=300,width=12,height=12,units="cm")
ggplot(hdat, aes(x=tot.wt.2017+0.1,y=tot.wt.2016+0.1)) +
  scale_x_log10(breaks=c(0.1,1,10,100,1000),labels=c(0,1,10,100,1000))+
  scale_y_log10(breaks=c(0.1,1,10,100,1000),labels=c(0,1,10,100,1000))+
  #geom_point(aes(shape=Outside.2016,colour=Outside.2016),size=2,show.legend=T)+
  geom_point() +
  #scale_shape_manual(values=20)+
  geom_abline(slope=1,intercept=0,lty=2) +
  xlab("2017 Harvest (g; log-scale)")+
  ylab("2016 Harvest (g; log-scale)")+
  labs(group="In Landscape")+
  coord_fixed()+
  theme(legend.position = "right")
dev.off()

## GRAPH: 2017 vs 2015 WITH Species Name 

ggplot(hdat, aes(x=tot.wt.2017+0.1,y=tot.wt.2015+0.1,label=hdat$SppName)) +
  scale_x_log10(breaks=c(0.1,1,10,100,1000),labels=c(0,1,10,100,1000))+
  scale_y_log10(breaks=c(0.1,1,10,100,1000),labels=c(0,1,10,100,1000))+
  geom_text_repel()+
  #geom_point(aes(shape=Outside.2016,colour=Outside.2016),size=2,show.legend=T)+
  geom_point() +
  #scale_shape_manual(values=20)+
  geom_abline(slope=1,intercept=0,lty=2) +
  xlab("2017 Harvest (g; log-scale)")+
  ylab("2015 Harvest (g; log-scale)")+
  labs(group="In Landscape")+
  coord_fixed()+
  theme(legend.position = "right")
#dev.off()

## GRAPH: 2017 vs 2015 WITHOUT Species names 

jpeg(filename ="C:\\Users\\susan\\Dropbox\\PhD\\Chp 3 Sust\\Results\\Harvest2015vs2017nolabs.jpg",res=300,width=12,height=12,units="cm")
ggplot(hdat, aes(x=tot.wt.2017+0.1,y=tot.wt.2015+0.1)) +
  scale_x_log10(breaks=c(0.1,1,10,100,1000),labels=c(0,1,10,100,1000))+
  scale_y_log10(breaks=c(0.1,1,10,100,1000),labels=c(0,1,10,100,1000))+
  #geom_point(aes(shape=Outside.2016,colour=Outside.2016),size=2,show.legend=T)+
  geom_point() +
  #scale_shape_manual(values=20)+
  geom_abline(slope=1,intercept=0,lty=2) +
  xlab("2017 Harvest (g; log-scale)")+
  ylab("2015 Harvest (g; log-scale)")+
  labs(group="In Landscape")+
  coord_fixed()+
  theme(legend.position = "right")
dev.off()
```


### Post-harvesting survey

Susan went into the plots and looked for any plants left behind, counted these, and identified (with the foragers) as to why it was left behind.

```{r unharvestedTable, echo=F}
# 
# pnh <- arrange(pnh,PlotNo,Species) %>% select(PlotNo,Species,Date,Edible.weight.count,CODE)
# 
# nHarvested <- ph %>% group_by(Species,PlotNo,Date) %>% summarise(nHarvested = sum(Edible.weight.count))
# 
# 
# pnh2 <- left_join(pnh,nHarvested,by=c("Species","PlotNo","Date")) 
# 
# 
# pnh.2015 <- filter(pnh2,Date<as.Date("2016-01-01")) 
# pnh.2016 <- filter(pnh2,Date>as.Date("2016-01-01"))
# 
# mat <- full_join(pnh.2015,pnh.2016,by=c("Species","PlotNo")) %>% select(-Date.x,-Date.y) %>% rename(nLeft2015=Edible.weight.count.x,nLeft2016=Edible.weight.count.y,nHarvested2015=nHarvested.x,nHarvested2016=nHarvested.y)
# 
# mat <- arrange(mat,PlotNo,Species) %>% filter(Species!="None")
# 
# mat[is.na(mat)] <- 0
# 
# 
# mat2 <- mutate(mat,Perc2015=round(nLeft2015/(nLeft2015+nHarvested2015)*100,0), Perc2016=round(nLeft2016/(nLeft2016+nHarvested2016)*100,0))
# mat2[is.na(mat2)] <- "-" 
# 
# mat2 <- select(mat2,PlotNo,Species,nHarvested2015,nLeft2015,Perc2015,CODE.x,nHarvested2016,nLeft2016,Perc2016,CODE.y)
# write.csv(mat2,"mat2.csv")
# 
# knitr::kable(mat2,align = 'clcccccccc')

```

